---
title: "Guest Data Analysis"
author: "Guest Data Unit"
date: "March 15th 2020"
fontsize: 10pt
output: 
  beamer_presentation: 
    colortheme: beaver
    fig_height: 5
    fonttheme: structuresmallcapsserif
    includes:
      in_header: header-Anthony.tex
    theme: AnnArbor
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```



<!----- Library----->

```{r}
library(tidyverse)
library(lubridate)
library(scales)
library(readxl)
library(ggrepel)
library(kableExtra)
#library(flextable)
#library(officer)
options(scipen = 999)
```


<!----- Read Data ------->

```{r}
# guest_data <- read_excel("C:\\Users\\LONGBRIDGE\\Documents\\Working.Directory\\Harvesters\\Data Captured - Sun 30th June, 2019.xlsx",
#                          sheet = "All Data",
#                         col_names = TRUE) %>%

 guest_data <- read_excel("Data Captured - Sun 15th Mar, 2020 - Anthony.xlsx",
                         sheet = "All Data",
                          col_names = TRUE) %>% 
  mutate(Timestamp = ymd_hms(Timestamp),
         #`Date of Birth` = ymd(`Date of Birth`), 
         `Date of Birth` = janitor::excel_numeric_to_date(as.numeric(`Date of Birth`)),
         Age = abs(round(time_length(interval(`Date of Birth`, Sys.Date()), "years"),0)),
         Age_Range = if_else(Age < 20, "<20 yrs", 
                             if_else(Age >= 20 & Age <= 25, "20-25 yrs",
                                     if_else(Age >= 26 & Age <= 35, "26-35 yrs",
                                             if_else(Age >= 36 & Age <= 45, "36-45 yrs", "46+")))))


guest_only <- guest_data %>% 
  filter(`Are you a?` != "New Convert")

convert_only <- guest_data %>% 
  filter(`Are you a?` == "New Convert")

```


## Guest analysis by Service Time

```{r}

# big_border = fp_border(color="blue", width = 2)
# border_v = fp_border(color="gray")
# border_h = fp_border(color="gray")
# 
 guest_only %>% 
   group_by(`Are you a?`, Service) %>% 
   count() %>% 
  # ungroup() %>% 
  # mutate(District = case_when(District == NA ~ "Unknown",
  #                             TRUE ~ District)) %>% 
   rename(Count = n) %>% 
   spread(Service, Count, fill = 0) %>% 
#   flextable() %>% 
#   border_remove() %>% 
#   border_outer(part="all", border = big_border ) %>% 
#   border_inner_h(part="all", border = border_h ) %>% 
#   border_inner_v(part="all", border = border_v ) %>%
#   bold(part = "header") %>%
#   autofit()
  
knitr::kable(., caption = "Guest count by service time and guest category", 
             "latex", booktabs = T)%>%
  kable_styling(full_width = F, latex_options = c("striped", "scale_down", "hold_position"))
```

## Guest analysis by District

```{r}

# big_border = fp_border(color="blue", width = 2)
# border_v = fp_border(color="gray")
# border_h = fp_border(color="gray")
# 
 guest_only %>% 
   group_by(`Are you a?`, District) %>% 
   count() %>% 
  ungroup() %>% 
  mutate(District = case_when(District == NA ~ "Unknown",
                              TRUE ~ District)) %>% 
   rename(Count = n) %>% 
   spread(District, Count, fill = 0) %>% 
#   flextable() %>% 
#   border_remove() %>% 
#   border_outer(part="all", border = big_border ) %>% 
#   border_inner_h(part="all", border = border_h ) %>% 
#   border_inner_v(part="all", border = border_v ) %>%
#   bold(part = "header") %>%
#   autofit()
  
knitr::kable(., caption = "Guest count by district and guest category", 
             "latex", booktabs = T)%>%
  kable_styling(full_width = F, latex_options = c("striped", "scale_down", "hold_position"))
```





## Guest analysis by guest category

```{r}


guest_only %>% 
  #filter(Age_Range != "NA") %>% 
  group_by(`Are you a?`) %>%
  summarise(Freq = n()) %>% 
  mutate(prop = Freq/sum(Freq)) %>% 
  filter(Freq != 0) %>% 
  
  ggplot(mapping = aes(x = 2, y = prop, fill = `Are you a?`))+
  geom_bar(width = 1, color = "white", stat = "identity") +
  xlim(0.5, 2.5) +
  coord_polar(theta = "y", start = 0) +
  theme_void() +
  scale_y_continuous(labels = percent) +
  geom_text(aes(label = paste0(round(prop*100, 1), "%")), size = 4, position = position_stack(vjust = 0.5)) +
  scale_fill_brewer(palette = "Reds", direction = 1) +
  #theme(axis.text.x = element_text(angle = 90), legend.position = "top")+
  labs(title = "Guest by category",
       x = "",
       y = "",
       fill = "Guest Category") +
  theme(legend.position = "bottom") 
```


## Guest analysis by gender


```{r}


guest_only %>% 
  filter(Gender != "NA") %>% 
  group_by(Gender) %>%
  summarise(Freq = n()) %>% 
  mutate(prop = Freq/sum(Freq)) %>% 
  filter(Freq != 0) %>% 
  
  ggplot(mapping = aes(x = 2, y = prop, fill = Gender))+
  geom_bar(width = 1, color = "white", stat = "identity", na.rm = TRUE) +
  xlim(0.5, 2.5) +
  coord_polar(theta = "y", start = 0) +
  theme_void() +
  scale_y_continuous(labels = percent) +
  geom_text(aes(label = paste0(round(prop*100, 1), "%")), size = 4, position = position_stack(vjust = 0.5)) +
  scale_fill_brewer(palette = "Reds", direction = 1) +
  #theme(axis.text.x = element_text(angle = 90), legend.position = "top")+
  labs(title = "Guest by gender category",
       x = "",
       y = "",
       fill = "Gender") +
  theme(legend.position = "bottom") 
```

## Guest by marital status

```{r}
guest_only %>% 
  filter(`Marital Status` != "NA") %>% 
  group_by(`Marital Status`) %>%
  summarise(Freq = n()) %>% 
  mutate(prop = Freq/sum(Freq)) %>% 
  filter(Freq != 0) %>% 
  
  ggplot(mapping = aes(x = 2, y = prop, fill = `Marital Status`))+
  geom_bar(width = 1, color = "white", stat = "identity") +
  xlim(0.5, 2.5) +
  coord_polar(theta = "y", start = 0) +
  theme_void() +
  scale_y_continuous(labels = percent) +
  geom_text(aes(label = paste0(round(prop*100, 1), "%")), size = 4, position = position_stack(vjust = 0.5)) +
  scale_fill_brewer(palette = "Reds", direction = 1) +
  #theme(axis.text.x = element_text(angle = 90), legend.position = "top")+
  labs(title = "Guest Marital Status",
       x = "",
       y = "",
       fill = "Status") +
  theme(legend.position = "bottom") 
```


## Guest analysis by age group

```{r eval=TRUE}


guest_only %>% 
  filter(Age_Range != "NA") %>% 
  group_by(Age_Range) %>%
  summarise(Freq = n()) %>% 
  mutate(prop = Freq/sum(Freq)) %>% 
  filter(Freq != 0) %>% 
  
  ggplot(mapping = aes(x = 2, y = prop, fill = Age_Range))+
  geom_bar(width = 1, color = "white", stat = "identity") +
  xlim(0.5, 2.5) +
  coord_polar(theta = "y", start = 0) +
  theme_void() +
  scale_y_continuous(labels = percent) +
  geom_text(aes(label = paste0(round(prop*100, 1), "%")), size = 3, position = position_stack(vjust = 0.5)) +
  scale_fill_brewer(palette = "Reds", direction = 1) +
  #theme(axis.text.x = element_text(angle = 90), legend.position = "top")+
  labs(title = "Guest by Age Group",
       x = "",
       y = "",
       fill = "Age Group") +
  theme(legend.position = "bottom") 
```

<!-- * We recorded a total guest ($1^{st}$ and $2^{nd}$ timers only) count of `r dim(guest_only)[1]`. with an average age of `r round(mean(guest_only$Age, na.rm = TRUE),0)` years. -->

## How did our guest hear about us?


```{r}


guest_only %>% 
  filter(`How did you hear of Harvesters?` != "NA") %>% 
  group_by(`How did you hear of Harvesters?`) %>%
  summarise(Freq = n()) %>% 
  mutate(prop = Freq/sum(Freq)) %>% 
  filter(Freq != 0) %>% 
  
  ggplot(mapping = aes(x = 2, y = prop, fill = `How did you hear of Harvesters?`))+
  geom_bar(width = 1, color = "white", stat = "identity") +
  xlim(0.5, 2.5) +
  coord_polar(theta = "y", start = 0) +
  theme_void() +
  scale_y_continuous(labels = percent) +
  geom_text(aes(label = paste0(round(prop*100, 1), "%")), size = 3, position = position_stack(vjust = 0.5)) +
  scale_fill_brewer(palette = "Reds", direction = 1) +
  #theme(axis.text.x = element_text(angle = 90), legend.position = "top")+
  labs(title = "Platform",
       x = "",
       y = "",
       fill = "Medium") +
  theme(legend.position = "bottom") 


```

<!-- ## Guest by service attendance -->

<!-- ```{r} -->
<!-- guest_only %>%  -->
<!--   #filter(`How did you hear of Harvesters?` != "NA") %>%  -->
<!--   group_by(Service) %>% -->
<!--   summarise(Freq = n()) %>%  -->
<!--   mutate(prop = Freq/sum(Freq)) %>%  -->
<!--   filter(Freq != 0) %>%  -->

<!--   ggplot(mapping = aes(x = 2, y = prop, fill = Service))+ -->
<!--   geom_bar(width = 1, color = "white", stat = "identity") + -->
<!--   xlim(0.5, 2.5) + -->
<!--   coord_polar(theta = "y", start = 0) + -->
<!--   theme_void() + -->
<!--   scale_y_continuous(labels = percent) + -->
<!--   geom_text(aes(label = paste0(round(prop*100, 1), "%")), size = 4, position = position_stack(vjust = 0.5)) + -->
<!--   scale_fill_brewer(palette = "Reds", direction = 1) + -->
<!--   #theme(axis.text.x = element_text(angle = 90), legend.position = "top")+ -->
<!--   labs(title = "Service Time", -->
<!--        x = "", -->
<!--        y = "", -->
<!--        fill = "Service") + -->
<!--   theme(legend.position = "bottom")  -->
<!-- ``` -->


## Decisions made by guest

```{r}
guest_only %>% 
  filter(`My decision today` != "NA") %>% 
  group_by(`My decision today`) %>%
  summarise(Freq = n()) %>% 
  mutate(prop = Freq/sum(Freq)) %>% 
  filter(Freq != 0) %>% 
  
  ggplot(mapping = aes(x = 2, y = prop, fill = `My decision today`))+
  geom_bar(width = 1, color = "white", stat = "identity") +
  xlim(0.5, 2.5) +
  coord_polar(theta = "y", start = 0) +
  theme_void() +
  scale_y_continuous(labels = percent) +
  geom_text(aes(label = paste0(round(prop*100, 1), "%")), size = 3, position = position_stack(vjust = 0.5)) +
  scale_fill_brewer(palette = "Reds", direction = 1) +
  #theme(axis.text.x = element_text(angle = 90), legend.position = "top")+
  labs(title = "Guest Decision",
       x = "",
       y = "",
       fill = "Decisions") +
  theme(legend.position = "bottom") 
```



## Guest by Location

```{r fig.width=12, fig.height=7}
guest_only %>% 
  filter(District != "NA") %>% 
  group_by(District) %>%
  summarise(Freq = n()) %>% 
  mutate(prop = Freq/sum(Freq)) %>% 
  filter(Freq != 0) %>% 
  
  ggplot(mapping = aes(x = reorder(District, prop), y = prop, fill = District))+
  geom_bar(width = 0.7, stat = "identity", show.legend = FALSE) +
  scale_y_continuous(labels = percent) +
  geom_text(aes(label = paste0(round(prop*100, 1), "%")), size = 3, position = position_stack(vjust = 0.5)) +
  scale_fill_brewer(palette = "Reds", direction = 1) +
  #theme(axis.text.x = element_text(angle = 90), legend.position = "top")+
  labs(title = "Guest by Location",
       x = "District",
       y = "",
       fill = "") +
  theme(legend.position = "bottom") +
  coord_flip() +
  theme_light()
```


## Appreciation

\includegraphics[width=1.90\textwidth,keepaspectratio]{Images/thank_you.jpg}

## Feedback

* For feedback, kindly reach the Head of Guest Data Unit via (**a.dayoajimuda@gmail.com**)
